\documentclass{resume}
\ResumeName{Guo Pengfei}

\begin{document}

\ResumeContacts{
  (+86) 187-6993-9178,%
  \ResumeUrl{mailto:pengfei.guo2001@gmail.com}{pengfei.guo2001@gmail.com}\\%
  \ResumeUrl{https://github.com/Michael-Jetson}{GitHub Homepage：https://github.com/Michael-Jetson},
  \ResumeUrl{https://pengfeiguo.top}{Homepage：https://pengfeiguo.top}
}

\ResumeTitle

\section{Research Interests}
3D Perception , Multi-modal Learning , Autonomous Vehicles


\section{Education}
%\ResumeItem
%[北京理工大学大学|硕士研究生]
%{北京理工大学}
%[\textnormal{网络空间安全，网络空间安全学院|}  学术型硕士研究生]
%[2021.09 - 2024.06（预计）]

%主要研究方向为\textbf{拜占庭共识算法}，在区块链和分布式系统领域方面有一定的研究和工程经验。\textbf{2024年应届生}。

\ResumeItem
{\textbf{North China Electric Power University}\\
\textnormal{Measurement and Control Technology and Instruments}}
[B.S. in Engineering]
[2019.09 - 2023.06]

\section{Experience}
\ResumeItemEn{Research Assistant}[ShanghaiTech University | SIST | VDI | 4DV Lab(Adviser:Ma Yuexin)][2023.07 - Now]
%\section[技术能力]{技术能力\protect\footnote{与求职岗位无关的技能省略或用灰色表示。}}
%\begin{itemize}
%  \item \textbf{前后端}: Rust, Golang, Python, MySQL, \GrayText{React, Vue.js, HTML/CSS}
%  \item \textbf{运维}: Docker, Linux, Shell, Kubernetes.
%  \item \textbf{关键词}: Tokio.rs, Consensus Algorithm, Vim, Git, Kafka, Markdown, \GrayText{Next.js}, \GrayText{\LaTeX}, \GrayText{Django}
%\end{itemize}

\section{Publications}
\begin{itemize}
  \item \textbf{Pengfei Guo}, Ziheng Hou, Wenhai Liu, Mengshuai Cao, Wenchao Wu. Family service robot intellisense and autonomous navigation technology research，ICAIR 2022，EI Search
  \item \textbf{Guo Pengfei}，Cao Mengshuai，Jiang Haoxuan，Su Yue，Yu Linzhu. A solar panel protection device for UAV. ZL 2022 2 1099247.X
  \item Zhang Shanchi，Tian Jingjia，Wu Jingwei，\textbf{Guo Pengfei}. A kind of UAV for agricultural monitoring. ZL 2022 2 2900534.2
  \item Wu Wenzhao,\textbf{Guo Pengfei},Li Zi,Cheng Haohua,Li Tianyu,Wu Chicheng,Yu Xiao,Shi Jianqin,Liu Feng,Ge Chuanmin. A kind of power equipment monitoring device. 202320149139.7
\end{itemize}

\section{Project}
\ResumeItemEn{\textbf{WildRefer}:3D Object Localization in Large-scale Dynamic Scenes with Multi-modal}
[Adviser:Ma Yuexin]
[2023.08 - Now]
\begin{itemize}
    \item Perception of dynamic large scenes using data in three modalities: image, point cloud and natural language to locate targets described by language
    \item Study the work on Visual Grounding and try to suggest improvements and test the expanded dataset of GPT.
\end{itemize}

\ResumeItemEn{Multi-Agent Environment and Modeling(collaboration with the Academy of Military Sciences)}
[Solution design and equipment selection]
[2021.11 - 2022.10] 

\begin{itemize}
  \item joined a team led by undergraduate supervisor for a project on multi-UAV collaborative ground target detection and search.
  \item involved in the project's solution design, hardware selection, and troubleshooting environment deployment.
  \item Communicate and negotiate with third party companies and the Military Academy of Sciences to advance the project.
\end{itemize}

%\ResumeItem{\ResumeUrl{https://github.com/BITNP/BIThesis}{\textbf{BIThesis} 北京理工大学毕设 LaTeX 模板集合(开源项目)}}
%[主要维护者]
%[2022.12 至今]
%\begin{itemize}
%  \item 根据相关排版要求，\textbf{利用 LaTeX3 (expl3) 设计了同时符合各个学位要求且支持灵活配置的宏包及多套模板}。
%  \item 需求开发和问题修复采用标准工作流，引入了回归测试与基于 Github Actions 的测试与持续集成。
%  \item 负责积极与学校进行沟通以审核模板；维护社区，及时响应用户的需求；撰写了大量文档。模板代码和使用手册分发至多个平台，仅 Github Releases 的模板下载量超过4000次。多届毕业生采用此模板进行毕业论文撰写。
%\end{itemize}大学生创新训练计划项目
\ResumeItemEn{Autonomous navigation robot based on SLAM and computer vision}[Project Technology Leader][2021.01 - 2023.05] 

\begin{itemize}
  \item Successfully applied for and chaired five projects of Da Chuang and two projects of the Hebei Provincial Department of Science and Technology for college students. During this period, he participated in competitions such as Intelligent Vehicle as a team leader.
  \item used SLAM and vision algorithms to enable aerial and ground robots to autonomously navigate and search for targets in complex environments, responsible for project design and programme deployment.
  \item learnt to use tools or frameworks such as PX4, ROS, PyTorch, etc. and successfully reproduced several classic papers.
\end{itemize}

\ResumeItemEn{RoboMaster Competition Infantry Robot Project}
[Leader]
[2022.09 - 2023.05] 

\begin{itemize}
  \item As the founder and captain of the school RoboMaster, the vision portion of the project was deployed and YOLOv5 was used to complete the target detection and targeting tasks.
\end{itemize}

\ResumeItem{\textbf{Kaggle：PetFinder.my - Pawpularity Contest}}[Bronze medal/Team member][2022.01 - 2022.03] 
\ResumeItem{\textbf{Kaggle：Image Matching Challenge 2023}}[Bronze medal/Team member][2023.05 - 2023.06] 
%\ResumeItemEn{\textbf{3D target detection project based on LiDAR point cloud characterization}}[][2023.06 - Now] 

%\begin{itemize}
%  \item Learn how to build, train and deploy code for point cloud target detection based on the open source project OpenPCDet
%  \item Learn relevant models and read papers, try to complete the replication independently
%\end{itemize}

\section{Challenges}

%\ResumeItem{2021年全国工程机器人大赛暨国际公开赛一等奖}[国家级/队员][2021.3 - 2021.10] 
%\begin{itemize}
%  \item \textbf{独立负责XXX业务后端的设计、开发、测试和部署。}通过 FaaS、Kafka 等平台实现站内信模板渲染服务。向上游提供 SDK 代码，增加或升级了多种离线和在线逻辑。
%  \item \textbf{参与XXX的需求分析，系统技术方案设计；完成需求开发、灰度测试、上线和监控。}
%\end{itemize}
\ResumeItemEn{2021 National Engineering Robotics Competition and International Open Competition First Prize}[National level/team members][2021.03 - 2021.10] 
\ResumeItemEn{2022 National Student Intelligent Vehicle Competition Second Prize}[National level/team leader][2022.06 - 2022.08] 
\ResumeItem{Participated in various competitions as a team member or team captain from 2020 to 2022, won seven provincial awards and more than ten university-level awards, presided over or participated in six projects (including two at the provincial level), two undergraduate science and technology projects of the Hebei Provincial Science and Technology Department (with one excellent and one passing grade), and also won the Science and Technology Innovation Excellence Award of NCEPU from 2021 to 2022.}


\section{Association Experience}
\ResumeItemEn{\textbf{Automation and Artificial Intelligence Club（A\&AI Club）}}[Founder and Technical Lead][2022.09 - 2023.06]
\begin{itemize}
    \item Communicating with teachers and colleges, as well as preparing for competitions, conducting technical training and screening, with the goal of winning high-level competitions, and sharing experiences on several occasions.
\end{itemize}

\section{Skills}
%\ResumeItem{自动化与人工智能俱乐部（A\&AI俱乐部）}[创始人兼技术负责人]
\begin{itemize}
    \item \textbf{Language：}CET4
    \item \textbf{Program：}C/C++，Python，MATLAB，LaTeX
    \item \textbf{Tools：}CMake，PyTorch，ROS，Git
\end{itemize}


\end{document}